 

### 2021-03-10 doc/manuscript/tables_figures/tables.Rmd
work on table

  pack_rows("Annual growth is jointly influenced by water, temperature, DBH, and time. ", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Drought limits tree growth, but the response to water is nonlinear.", 3, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Temperature has predominantly negative, nonlinear effects on growth.", 6, 9, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("DBH", 10, 13, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%

>>>>

  pack_rows("Annual growth is jointly influenced by water, temperature, DBH, and time. ", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Drought limits tree growth, but the response to water is nonlinear.", 6, 8, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Temperature has predominantly negative, nonlinear effects on growth.", 9, 12, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Growth rate, by any metric, varies nonlinearly with DBH.", 13, 16, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
